---
title: "Imputation data"
author: "Ruby Xiong"
format: html
editor: source
---

```{r}
library(GammaGateR)
library(data.table)
library(gridExtra)
library(ggpubr)
library(car)
library(RESI)
library(emmeans)
library(parallel)
library(hrbrthemes)
library(ggplot2)
library(fossil)
library(dplyr)
library(nlme)
library(glmnet)
library(modelr)
library(xgboost)
library(dplyr)
library(caret)
library(hdrcde)
library(reshape2)
```

## Load and normalize expressions

Dataset: https://data.mendeley.com/datasets/mpjzbtfgfr/1

```{r loadData}
dataSchurch<- read.csv(file='/media/disk2/atlas_mxif/data/CRC_clusters_neighborhoods_markers.csv', header = TRUE)
originalNames <- names(dataSchurch)
markers <- originalNames[grep("\\.\\.\\.", originalNames)] |>
          strsplit("\\.\\.\\.") |> lapply("[[",1) |> unlist()
marker_datanames <- originalNames[grep("\\.\\.\\.", originalNames)]

```

Paper (https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3440263) mentions that + "profiling of 140 tissue regions from 35 advanced-stage colorectal cancer (CRC) patients with 56 protein markers simultaneously" + "we selected cohorts of 17 CLR and 18 DII patients"

```{r}
length(markers)
length(unique((dataSchurch$File.Name)))#region
length(unique((dataSchurch$patients)))#patient
ifelse(table(dataSchurch$groups, dataSchurch$patients)[1,], 1, 0) # CLR patients - 1, DII patients - 2
# data size
hist(table(dataSchurch$File.Name))
hist(table(dataSchurch$patient))
table(dataSchurch$patients, dataSchurch$File.Name) # each patient has several regions
# what is TMA_AB?? it looks like some sort of characteristic of a specific region, but within patient can have different ABs
table(dataSchurch$TMA_AB, dataSchurch$File.Name)
```

### Normalize Cell Expression

```{r}
allMarkers = markers
nzNormedMarkers = paste0('nzNorm_',allMarkers)
dataSchurch = do.call(rbind, lapply(split(dataSchurch, dataSchurch$TMA_AB), function(df){df[,nzNormedMarkers] = log10(1+sweep(df[,marker_datanames], 2, colMeans(replace(df[,marker_datanames], df[,marker_datanames]==0, NA), na.rm = TRUE ), FUN = '/' ) ); df }) )
slides <- unique(dataSchurch$patients)
```

# simple plot check up

```{r}
par(pty="s")
plot(dataSchurch$X_withinTile.X_withinTile[dataSchurch$File.Name=="reg001_A"],
            dataSchurch$Y_withinTile.Y_withinTile[dataSchurch$File.Name=="reg001_A"],pch=16, cex=0.5)
```


```{r}
names(dataSchurch)
```

# Fold Split

```{r}
# 18 training slides, 17 testing slides # even split
CLR_patients <- slides[table(dataSchurch$patients, dataSchurch$groups)[,1]>0]
DII_patients <- slides[table(dataSchurch$patients, dataSchurch$groups)[,2]>0]
set.seed(1)
## training 
trainPatients <- c(CLR_patients[sample(1:17, 12)], DII_patients[sample(1:18, 12)])
## testing
testPatients <-  setdiff(slides, trainPatients)
## slide - patient correspondence
SlidePatient <- dataSchurch %>% group_by(patients, File.Name) %>% reframe()
## training slides
trainSlide <- SlidePatient$File.Name[which(SlidePatient$patients %in% trainPatients)]
testSlide <- SlidePatient$File.Name[which(SlidePatient$patients %in% testPatients)]

```

# functions for analysis

Testing out with CD20

```{r function_createFoldData}
marker="CD20"
createFoldData <- function(dat=dataSchurch, slideTrain=slideTrain, marker="MUC5AC"){
  # normalized expression name in the dataset
  nzmarkername <- paste("nzNorm", marker, sep="_")
  #define predictor and response variables in testing set. Use the common markers for all 3 batches as the prediction variables
  commons_regress <- nzNormedMarkers[nzNormedMarkers!=nzmarkername]
  HTA_train1 <- as.matrix(dat[dat$File.Name%in%slideTrain,commons_regress])
  # Need to code tissue type and tumor (binary) as discrete numbers to run XGBoost
  HTA_train2 <- cbind(HTA_train1, dat[dat$File.Name%in%slideTrain,"groups"])
  HTA_train_marker <- dat[dat$File.Name%in%slideTrain, nzmarkername]
  return(list(HTA_train1, HTA_train2, HTA_train_marker, dat_original = dat[dat$File.Name%in%slideTrain, ]))
}
```

```{r function_imputation}
imputation <- function(marker="CD20", trainSlides=trainSlide, testSlides=testSlide, 
                       dataset=dataSchurch, n.imp=10){
  trainData <- createFoldData(dat=dataset, 
                              slideTrain = trainSlides, 
                              marker = marker)
  cv_model2 <- glmnet:::cv.glmnet(trainData[[2]], trainData[[3]], alpha = 1, nfolds = 5)
  # find optimal lambda value that minimizes test MSE
  best_lambda2 <- cv_model2$lambda.min
  best_model2 <- glmnet::glmnet(trainData[[2]], trainData[[3]], alpha = 1, lambda = best_lambda2)
  testData <- createFoldData(dat=dataset, 
                            slideTrain = testSlides, 
                            marker = marker)
  Yhat.test <- as.numeric(
    predict(best_model2,newx=testData[[2]],s= best_lambda2))
  
  # slide-specific calibration
  calibY <- c()
  calibYhat <- c()
  calibSlides <- c()
  for(i in trainSlides){
    trainslidei <- setdiff(trainSlides,i)
    trainDatai <- createFoldData(dat=dataset, 
                                slideTrain = trainslidei, 
                                marker = marker)
    
    # model with tumor info
    cv_model2 <- glmnet:::cv.glmnet(trainDatai[[2]], trainDatai[[3]], alpha = 1, nfolds = 5)
    # find optimal lambda value that minimizes test MSE
    best_lambda2 <- cv_model2$lambda.min
    best_model2 <- glmnet::glmnet(trainDatai[[2]], trainDatai[[3]], alpha = 1, lambda = best_lambda2)
    caliData <- createFoldData(dat=dataset, 
                               slideTrain = i, 
                               marker = marker)
    Yhat <- as.numeric(
      predict(best_model2,newx=caliData[[2]],s= best_lambda2))
    
    calibY <- c(calibY, caliData[[3]])
    calibYhat <- c(calibYhat, Yhat)
    calibSlides <- c(calibSlides, rep(i, length(Yhat)))
  }
  
  ################################
  ########## Use imimp ###########
  ################################
  
  imp.simple <- imimp(Yhat.test, calibYhat , calibY, cdeType = "simple", x.mar = 50, y.mar=100, n.mi=n.imp)
  imp.local<- imimp(Yhat.test, calibYhat, calibY, cdeType = "local", n.mi=n.imp)
  
  SlideGroup <- dataSchurch %>% group_by(File.Name, groups) %>% reframe()
  calibSlides_CLR <- which(calibSlides %in% (unlist(subset(SlideGroup, groups==1, File.Name))))
  calibSlides_DII <- which(calibSlides %in% (unlist(subset(SlideGroup, groups==2, File.Name))))
  
  testSlidesAll <- dataSchurch$File.Name[dataSchurch$patients %in% testPatients]
  testSlides_CLR <- which(testSlidesAll %in% (unlist(subset(SlideGroup, groups==1, File.Name))))
  testSlides_DII <- which(testSlidesAll %in% (unlist(subset(SlideGroup, groups==2, File.Name))))
  
  imp.bySample <- matrix(NA, nrow=length(testSlidesAll), ncol=n.imp)

  imp.bySample[testSlides_CLR,] <- imimp(Yhat.test[testSlides_CLR], calibYhat[calibSlides_CLR],
                    calibY[calibSlides_CLR], cdeType = "bySample",
                    x.mar = 50, y.mar=100, 
                    sampleID=list(calibSlides[calibSlides_CLR], testSlidesAll[testSlides_CLR]), n.mi=n.imp)
  
  imp.bySample[testSlides_DII,] <-imimp(Yhat.test[testSlides_DII], calibYhat[calibSlides_DII],
                    calibY[calibSlides_DII], cdeType = "bySample",
                    x.mar = 50, y.mar=100, 
                    sampleID=list(calibSlides[calibSlides_DII], testSlidesAll[testSlides_DII]), n.mi=n.imp)

  
  imp.list <- list(Yhat, imp.simple, imp.local, imp.bysample)
  save(imp.list, file=paste0("~/ImageImputation/",paste(substitute(dataset)),"fit", marker, ".RData"))

}
```

# plot: imputation quantile v.s. real quantile

```{r function_summary_quantile}

# library(tidyverse)
# library(tidyr)
# library(tibble)
library(reshape2)
# detach(package:plyr)
single_data_process <- function(input.data){
    names(data.subset.test) <- c("value", "slides", "groups")
    real.quantiles.test <- data.subset.test %>% 
      group_by(slides) %>%  
      reframe(groups=first(groups),
              quantile = scales::percent(c(0.9, 0.95, 0.99)),
              real_value = quantile(value, c(0.9, 0.95, 0.99)))
    return(real.quantiles.test)
}



summary_quantile <- function(imp.result=imp.list.strat, marker=marker, dataset=dataSchurch, testSlides=testSlides){
  yhat.test <- imp.result[[1]]
  imp.result=imp.result[2:4]
  slides.vec <- dataset$File.Name[dataset$File.Name %in% testSlides]
  quantile.list.strat <- lapply(imp.result, function(imp.mat){
    imp.df <- data.frame(imp.mat, slides=slides.vec)
    imp.df$groups <- dataset$groups[which(dataset$File.Name %in% testSlides)]
    imp.vec <- melt(as.data.table(imp.df), id.vars = c("slides","groups"), variable.name = "im")
    quantile.df <- as.data.frame(imp.vec %>%
                    group_by(slides, im, groups) %>%
                    reframe(quantile = scales::percent(c(0.9, 0.95, 0.99)),
                    value = quantile(value, c(0.9, 0.95, 0.99))))
    return(quantile.df)
  })
  quantile.list.df.strat <- do.call(rbind, quantile.list.strat )
  quantile.list.df.strat$methods <- rep(c("simple", "local", "bySample"), each=(nrow(quantile.list.df.strat)/3))
  quantile.imp.summary.strat  <- as.data.frame(quantile.list.df.strat  %>% group_by(quantile, im, groups, methods) %>% reframe(means=mean(value)))
  # test data true
  real.quantiles.test <- single_data_process(dataset[which(dataset$File.Name %in% testSlide),c(paste0("nzNorm_", marker), "File.Name", "groups")])
  # training data true
  real.quantiles.train <- single_data_process(dataset[which(!(dataset$File.Name %in% testSlide)),c(paste0("nzNorm_", marker), "File.Name", "groups")])
  # yhat
  quantiles.yhat <- single_data_process(data.frame(yhat.test, dataset[which(dataset$File.Name %in% testSlide),c("File.Name", "groups")]))
  
  ll <- list(quantile.list.df.strat, real.quantiles.test, real.quantiles.train, quantiles.yhat)

save(ll, file = paste0("~/ImageImputation/plots/dataSchurch", marker,"quantileIMP.RData"))
}
```

TARGET PARAMETER: MEAN QUANTILE (v.s. example mean difference)

```{r function_descriptive_quantiles}
marker="CD20"
n.imp <- 10

var.calc <- function(qunatiledf){
  # within imputation: formula 9.2
  n.slides <- unique(qunatiledf$slides)
  within.var <- as.data.frame(qunatiledf %>% group_by(methods, quantile, im)%>%dplyr::summarize(SEi = se.sq(value), .groups = "keep"))
  within.var.pool <- as.data.frame(within.var%>%group_by(methods, quantile)%>%dplyr::summarize(VARW = mean(SEi), .groups = "keep"))
  # between imputation: formula 9.3
  between.var <- as.data.frame(qunatiledf %>% group_by(methods, quantile, im)%>%dplyr::reframe(meanImp = mean(value), .groups = "keep"))
  between.var.pool <- as.data.frame(between.var%>%group_by(methods, quantile)%>%dplyr::summarize(VARB = var(meanImp), means=mean(meanImp), .groups = "keep"))
  # pool variance: formula 9.4
  library(dplyr)
  all.vars <- left_join(within.var.pool, between.var.pool, by=c("methods", "quantile"))
  all.vars$VARB <- all.vars$VARB
  all.vars$vars <- all.vars$VARW+all.vars$VARB*((n.imp+1)/n.imp)
  # calculate df
  source("~/ImageImputation/dfCalc.R")
  all.vars.df <- dfCalc(all.vars$VARB, all.vars$vars, n.imp ,length(testSlides), 1)
  all.vars$tval95 <- qt(0.975, all.vars.df)
  return(all.vars)
}

se.sq <- function(a){sd(a)^2/length((a))}

descriptive_quantiles <- function(result.list, n.testSlide=44, n.trainslide=96){
  impQuantile <- result.list[[1]]
  trueQuantiletest <- result.list[[2]]
  trueQuantiletrain <- result.list[[3]]
  QuantileYhat <- result.list[[4]]

  all.vars.strat <- var.calc(qunatiledf=impQuantile)
  # real quantile mean and variance
  true.plot.test <- trueQuantiletest %>% group_by(quantile)%>%dplyr::summarise(means=mean(real_value), vars=se.sq(real_value), methods="true_test") %>% as.data.frame()
  true.plot$tval95 <- qt(0.975, (length(n.testSlide)-1))
  
  true.plot.train <- trueQuantiletrain %>% group_by(quantile)%>%dplyr::summarise(means=mean(real_value), vars=se.sq(real_value), methods="true_train") %>% as.data.frame()
  true.plot$tval95 <- qt(0.975, (length(n.trainSlide)-1))
  
  yhatPlot <- QuantileYhat %>% group_by(quantile)%>%dplyr::summarise(means=mean(real_value), vars=se.sq(real_value), methods="yhat") %>% as.data.frame()
  yhatPlot$tval95 <- qt(0.975, (length(n.testSlide)-1))

  df.plot.strat <- rbind(true.plot.train, true.plot.test, yhatPlot, all.vars.strat[,c("methods", "quantile", "means", "vars", "tval95")])
  df.plot.strat$sd <- sqrt(df.plot$vars)

  p = ggplot() +
    geom_errorbar(data=df.plot,aes(xmin=means-tval95*sd, xmax=means+tval95*sd, y=methods), width=.2)+
    geom_point(data=df.plot,aes(x=means, y=methods))+facet_wrap(~quantile, scales = "free_x") +
    ggtitle(marker)+theme_bw()
  ggsave(p, file=paste0("~/ImageImputation/figure/RubinPool", marker, ".png"), width=9.85, height=7.79, dpi=300)

  # plot mean and pooled var by group
all.vars.CLR.strat <- cbind(var.calc(qunatiledf=subset(quantile.list.df.strat, groups==1)),groups=1)
all.vars.DII.strat <- cbind(var.calc(qunatiledf=subset(quantile.list.df.strat, groups==2)),groups=2)
true.plot.bygroup <- trueQuantile %>%
  group_by(quantile, groups)%>%
  dplyr::summarise(means=mean(real_value), vars=se.sq(real_value), methods="true") %>%
  as.data.frame()
true.plot.bygroup$tval95 <- qt(0.975, (length(testSlides)-1))

df.plot.bygroup <- 
  rbind(true.plot.bygroup[,c("methods", "quantile", "means", "vars", "tval95", "groups")], 
  all.vars.CLR.strat[,c("methods", "quantile", "means", "vars", "tval95", "groups")],
  all.vars.DII.strat[,c("methods", "quantile", "means", "vars", "tval95","groups")])

df.plot.bygroup$sd <- sqrt(df.plot.bygroup$vars)
df.plot.bygroup$groups <- factor(df.plot.bygroup$groups, label=c("CLR", "DII"))
p = ggplot() +
  geom_errorbar(data=df.plot.bygroup,aes(xmin=means-tval95*sd, xmax=means+tval95*sd, y=methods, color=groups), width=.2)+
  geom_point(data=df.plot.bygroup,aes(x=means, y=methods, color=groups))+facet_wrap(~quantile, scales = "free_x") +
  ggtitle(marker)+theme_bw()

  ggsave(p, file=paste0("~/ImageImputation/figure/RubinPoolbygroup", marker, ".png"), width=9.85, height=7.79, dpi=300)
  
## variance bar plot
var.plot.strat <- reshape2::melt(all.vars.strat[,c(1,2,3,4,6)], id.vars=c("methods", "quantile"))
# add true data varW
var.plot.strat <- rbind(var.plot.strat, 
                  data.frame(methods="true", quantile=var.plot.strat$quantile,
                                       variable="VARW", value=true.plot$vars),
                  data.frame(methods="true", quantile=var.plot.strat$quantile,
                                       variable="vars", value=true.plot$vars))

# diff.plot$type <- ifelse(diff.plot$variable=="vars", "total", "separate")
p <- ggplot(var.plot.strat, aes(fill=variable, y=value, x=methods)) + 
    geom_bar(position="dodge", stat="identity")+
  facet_grid(rows=vars(variable),
             cols=vars(quantile), scales = "free") +theme_ipsum()+scale_x_discrete(guide = guide_axis(angle = 45))

  ggsave(p, file=paste0("~/ImageImputation/figure/RubinPoolVarBarPlot", marker, ".png"), width=9.85, height=7.79, dpi=300)
}
```

GEE difference stratified

```{r function gee_plot}
library(gee)
library(geepack)

gee_plot <- function(result.list, SlidePatient=SlidePatient){
  quantile.list.df.strat <- result.list[[1]]
  trueQuantiletest <- result.list[[2]]
  trueQuantiletrain <- result.list[[3]]

  quantile3 <- unique(quantile.list.df.strat$quantile)

# imputation mean
  impMeans <- as.data.frame(quantile.list.df.strat %>% group_by(quantile, slides, methods) %>% reframe(means=mean(value)))
  SlidePatientGroup <- dataSchurch %>% group_by(patients, File.Name, groups) %>% reframe()
impMeans <- left_join(impMeans, SlidePatientGroup, by=join_by(slides==File.Name))

  trueQuantiltest <- left_join(trueQuantiletest, SlidePatient, by=join_by(slides==File.Name))
  trueQuantiltrain <- left_join(trueQuantiletrain, SlidePatient, by=join_by(slides==File.Name))

  df.plot.geemean <- data.frame(quantile=rep(c("90%", "95%", "99%"), 5),
                      means=NA, sd=NA, stats=NA,
                      methods=rep(c("test", "train","mean","simple" , "local" , "bySample"), each=3))


# pool parameter estimates with Rubin's:
# mean: mean parameter estimate
# VarB: the variance of parameter estimate mean, of each imputation
# VarW: the mean of parameter estimate variance, of each imputation
quantile.list.df.strat <- left_join(quantile.list.df.strat, SlidePatient, by=join_by(slides==File.Name))
for(i in quantile3){
  for(singleData.i in 2:4){
    singleData <- result.list[[singleData.i]]
    method <- c("test", "train","mean")[(singleData.i-1)]
    singleData <- left_join(singleData, SlidePatient, by=join_by(slides==File.Name))
    m0 <- gee(real_value ~ 1, id=patients, family='gaussian',
            corstr = "exchangeable", data=subset(trueQuantile, quantile==i))
    idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods==method
    df.plot.geemean$means[idx] <- m0$coefficients
    df.plot.geemean$sd[idx] <- sqrt(m0$robust.variance)
    df.plot.geemean$stats[idx] = qnorm(0.975)
  }
  
  for(m in c("simple", "local", "bySample")){
    n.imp <- length(levels(quantile.list.df.strat$im))
    m0.param <- data.frame(mean=rep(NA, n.imp), SE=rep(NA, n.imp))
    for(ii in 1:n.imp){
      m0 <- gee(value ~ 1, id=patients, family='gaussian', corstr = "exchangeable", 
            data=subset(quantile.list.df.strat, (quantile==i&methods==m&im==paste0("X",ii))))
      m0.param[ii,"mean"] <- m0$coefficients
      m0.param[ii,"SE"] <- summary(m0)$coefficients[4]
    }
  idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods==m
  df.plot.geemean$means[idx] <- mean(m0.param$mean)
  VARB <- var(m0.param$mean)
  vars <- sqrt(var(m0.param$mean)*(n.imp+1)/n.imp+mean((m0.param$SE)^2))
  df.plot.geediff$sd[idx] <- vars
  df.plot.geediff$stats[idx] <- qt(0.975, dfCalc(VARB, vars, 10 , 44, 2))
  }
}

p = ggplot() +
  geom_errorbar(data=df.plot.geemean,aes(xmin=means-stats*sd, xmax=means+stats*sd, y=methods), width=.2)+
  geom_point(data=df.plot.geemean,aes(x=means, y=methods))+facet_wrap(~quantile, scales = "free_x") +
  ggtitle(paste0(marker, ": GEE Means"))+theme_bw()
ggsave(p, file=paste0("~/ImageImputation/figure/DataSchurchGEEMean", marker,"_",test.i, ".png"), width=4, height=3.5, dpi=300)

gee.results <- list()
df.plot.geediff <- df.plot[,c("quantile", "means", "sd","methods")]

for(i in quantile3){
  
  for(singleData.i in 2:4){
    singleData <- result.list[[singleData.i]]
    method <- c("test", "train","mean")[(singleData.i-1)]
    singleData <- left_join(singleData, SlidePatient, by=join_by(slides==File.Name))
    m0 <- gee(real_value ~ groups, id=patients, family='gaussian',
            corstr = "exchangeable", data=subset(trueQuantile, quantile==i))
    idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods==method
    df.plot.geemean$means[idx] <- m0$coefficients[2]
    df.plot.geemean$sd[idx] <- sqrt(m0$robust.variance)[2,2]
    df.plot.geemean$stats[idx] = qnorm(0.975)
  }
  
  for(m in c("simple", "local", "bySample")){
    n.imp <- length(levels(quantile.list.df.strat$im))
    m0.param <- data.frame(mean=rep(NA, n.imp), SE=rep(NA, n.imp))
    for(ii in 1:n.imp){
      m0 <- gee(value ~ groups, id=patients, family='gaussian', corstr = "exchangeable", 
            data=subset(quantile.list.df.strat, (quantile==i&methods==m&im==paste0("X",ii))))
      m0.param[ii,"mean"] <- m0$coefficients[2]
      m0.param[ii,"SE"] <- summary(m0)$coefficients[2,4]
    }
    
  idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods==m
  df.plot.geediff$means[idx] <- mean(m0.param$mean)
  VARB <- var(m0.param$mean)
  vars <- sqrt(var(m0.param$mean)*(n.imp+1)/n.imp+mean((m0.param$SE)^2))
  df.plot.geediff$sd[idx] <- vars
  df.plot.geediff$stats[idx] <- qt(0.975, dfCalc(VARB, vars, 10 , 44, 2))
  }
}

p = ggplot() +
  geom_errorbar(data=df.plot.geediff,aes(xmin=means-sd*stats, xmax=means+sd*stats, y=methods), width=.2)+
  geom_point(data=df.plot.geediff,aes(x=means, y=methods))+facet_wrap(~quantile, scales = "free_x") +
  ggtitle(paste0(marker, ": GEE Difference"))+theme_bw()
  ggsave(p, file=paste0("~/ImageImputation/figure/DataSchurchGEEDiff", marker,"_",test.i, ".png"), width=4, height=3.5, dpi=300)
}

```

# Test Data Check

```{r}
qq.plot <- list()
methods=c("simple", "local", "bySample")
quantiles.list <- list()
testSlidesAll <- dataSchurch$File.Name[dataSchurch$File.Name %in% testSlides]
for(test.i in (testSlides[c(1,2, 17,18)])){
  quantiles.list <- list()
  idx <- which(testSlidesAll==test.i)
  for(m in 1:length(imp.list.strat)){
  method.i <- imp.list.strat[[m]]
  m.i <- methods[m]
  quantiles.list[[m]] <- apply(method.i[idx,], 2, function(x){quantile(x, ((1:500)/500))})
  }
  quantiles.list <- as.data.frame(do.call(rbind,quantiles.list))
  quantiles.list$methods <- rep(methods, each=500)
  quantiles.list$xreal <- quantile(dataSchurch$nzNorm_CD20[dataSchurch$File.Name==test.i], ((1:500)/500))
  quantiles.df <- reshape2::melt(quantiles.list, id.vars=c("methods", "xreal"))
  
  quantiles.df$methods <- factor(quantiles.df$methods)
  p <- ggplot(data=quantiles.df) +
       geom_line(aes( x=xreal,y=value, group=interaction(variable, methods), color=methods), alpha=0.5) + geom_abline(intercept=0, slope=1)+theme_ipsum()
  ggsave(p, file=paste0("~/ImageImputation/figure/DataSchurchQQ", marker,"_",test.i, ".png"), width=4, height=3.5, dpi=300)
}
```


# loops at different marker

```{r}
markers <- c("CD20", "CD38", "CD138", "CD4", "CD68", "CD8")

for(marker in markers){
  trainData <- createFoldData(dat=dataSchurch, 
                            slideTrain = trainSlides, 
                            marker = marker)
cv_model2 <- glmnet:::cv.glmnet(trainData[[2]], trainData[[3]], alpha = 1, nfolds = 5)
# find optimal lambda value that minimizes test MSE
best_lambda2 <- cv_model2$lambda.min
best_model2 <- glmnet::glmnet(trainData[[2]], trainData[[3]], alpha = 1, lambda = best_lambda2)
testData <- createFoldData(dat=dataSchurch, 
                          slideTrain = testSlides, 
                          marker = marker)
Yhat.test <- as.numeric(
  predict(best_model2,newx=testData[[2]],s= best_lambda2))

# slide-specific calibration
calibY <- c()
calibYhat <- c()
calibSlides <- c()
for(i in trainSlides){
  trainslidei <- setdiff(trainSlides,i)
  trainDatai <- createFoldData(dat=dataSchurch, 
                              slideTrain = trainslidei, 
                              marker = marker)
  
  # model with tumor info
  cv_model2 <- glmnet:::cv.glmnet(trainDatai[[2]], trainDatai[[3]], alpha = 1, nfolds = 5)
  # find optimal lambda value that minimizes test MSE
  best_lambda2 <- cv_model2$lambda.min
  best_model2 <- glmnet::glmnet(trainDatai[[2]], trainDatai[[3]], alpha = 1, lambda = best_lambda2)
  caliData <- createFoldData(dat=dataSchurch, 
                             slideTrain = i, 
                             marker = marker)
  Yhat <- as.numeric(
    predict(best_model2,newx=caliData[[2]],s= best_lambda2))
  
  calibY <- c(calibY, caliData[[3]])
  calibYhat <- c(calibYhat, Yhat)
  calibSlides <- c(calibSlides, rep(i, length(Yhat)))
}

################################
########## Use imimp ###########
################################

imp.simple <- imimp(Yhat.test, calibYhat , calibY, cdeType = "simple", x.mar = 50, y.mar=100)
imp.local<- imimp(Yhat.test, calibYhat, calibY, cdeType = "local")
imp.bysample<-imimp(Yhat.test, calibYhat , calibY, cdeType = "bySample",
                    x.mar = 50, y.mar=100, sampleID=list(as.character(calibSlides), as.character(dataSchurch$File.Name[dataSchurch$patients %in% testPatients])))
imp.list <- list(imp.simple, imp.local, imp.bysample)
save(imp.list, file=paste0("~/ImageImputation/Schurchfit", marker, ".RData"))

slides.vec <- dataSchurch$File.Name[dataSchurch$File.Name %in% testSlides]
# library(tidyverse)
# library(tidyr)
# library(tibble)
library(reshape2)
# detach(package:plyr)
quantile.list <- lapply(imp.list, function(imp.mat){
  imp.df <- data.frame(imp.mat, slides=slides.vec)
  imp.df$groups <- dataSchurch$groups[which(dataSchurch$File.Name %in% testSlides)]
  imp.vec <- melt(as.data.table(imp.df), id.vars = c("slides","groups"), variable.name = "im")
  quantile.df <- as.data.frame(imp.vec %>%
                  group_by(slides, im, groups) %>%
                  reframe(quantile = scales::percent(c(0.9, 0.95, 0.99)),
                  value = quantile(value, c(0.9, 0.95, 0.99))))
  return(quantile.df)
})
quantile.list.df <- do.call(rbind, quantile.list)
quantile.list.df$methods <- rep(c("simple", "local", "bySample"), each=(nrow(quantile.list.df)/3))
quantile.imp.summary <- as.data.frame(quantile.list.df %>% group_by(quantile, im, groups, methods) %>% reframe(means=mean(value))
)
data.subset <- dataSchurch[which(dataSchurch$File.Name %in% testSlides),c(paste0("nzNorm_", marker), "File.Name", "groups")]
names(data.subset) <- c("value", "slides", "groups")
real.quantiles <- data.subset %>% 
  group_by(slides) %>%  
  reframe(groups=first(groups),
            quantile = scales::percent(c(0.9, 0.95, 0.99)),
            real_value = quantile(value, c(0.9, 0.95, 0.99)))
real.quantiles.summary <- as.data.frame(real.quantiles %>% group_by(quantile,groups) %>% summarise(means=mean(real_value), .groups = "keep")
)
ll <- list(quantile.list.df, real.quantiles)

save(ll, file = paste0("~/ImageImputation/plots/dataSchurch", marker,"quantileIMP.RData"))
print(marker)
}

plot.df.list <- list()
for(marker in markers){
  load(paste0("~/ImageImputation/plots/dataSchurch", marker,"quantileIMP.RData"))
  n.imp <- 10
  impQuantile <- ll[[1]]
  trueQuantile <- ll[[2]]
  se.sq <- function(a){sd(a)^2/length((a))}
    
  var.calc <- function(qunatiledf){
    # within imputation: formula 9.2
    n.slides <- unique(qunatiledf$slides)
    within.var <- as.data.frame(qunatiledf %>% group_by(methods, quantile, im)%>%dplyr::summarize(SEi = se.sq(value), .groups = "keep"))
    within.var.pool <- as.data.frame(within.var%>%group_by(methods, quantile)%>%dplyr::summarize(VARW = mean(SEi), .groups = "keep"))
    # between imputation: formula 9.3
    between.var <- as.data.frame(qunatiledf %>% group_by(methods, quantile, im)%>%dplyr::reframe(meanImp = mean(value), .groups = "keep"))
    between.var.pool <- as.data.frame(between.var%>%group_by(methods, quantile)%>%dplyr::summarize(VARB = var(meanImp), means=mean(meanImp), .groups = "keep"))
    # pool variance: formula 9.4
    library(dplyr)
    all.vars <- left_join(within.var.pool, between.var.pool, by=c("methods", "quantile"))
    all.vars$VARB <- all.vars$VARB
    all.vars$vars <- all.vars$VARW+all.vars$VARB*((n.imp+1)/n.imp)
    # calculate df
    source("~/ImageImputation/dfCalc.R")
    all.vars.df <- dfCalc(all.vars$VARB, all.vars$vars, n.imp ,length(testSlides), 1)
    all.vars$tval95 <- qt(0.975, all.vars.df)
    return(all.vars)
  }
  all.vars <- var.calc(qunatiledf=impQuantile)
  # real quantile mean and variance
  true.plot <- trueQuantile %>% group_by(quantile)%>%dplyr::summarise(means=mean(real_value), vars=se.sq(real_value), methods="true") %>% as.data.frame()
  true.plot$tval95 <- qt(0.975, (length(testSlides)-1))
  
  df.plot <- rbind(true.plot, all.vars[,c("methods", "quantile", "means", "vars", "tval95")])
  df.plot$sd <- sqrt(df.plot$vars)
  df.plot$marker <- marker
  plot.df.list[[marker]] <- df.plot
}
plot.markerAll.df <- do.call(rbind, plot.df.list) %>% as.data.frame()
plot.markerAll.df$methods <- factor(plot.markerAll.df$methods , levels = c("true", "simple", "local", "bySample"))

```

```{r fig.align="center", echo = FALSE,fig.height = 10, fig.width=7}
ggplot() +
  geom_errorbar(data=plot.markerAll.df,aes(ymin=means-tval95*sd, ymax=means+tval95*sd, x=marker, group=methods), position=position_dodge(width=0.4),width=.15)+
  geom_point(data=plot.markerAll.df,aes(y=means, x=marker, shape=methods), position=position_dodge(width=0.4))+facet_wrap(~quantile, scales = "free_x", ncol=3) +
  ggtitle("Imputation Quantiles")+theme_bw()+coord_flip()
ggsave(p, file=paste0("~/ImageImputation/figure/RubinPoolAllmarker.png"), width=9.85, height=7.79, dpi=300)
```

# loops at different marker, stratified

```{r}
markers <- c("CD20", "CD38", "CD138", "CD4", "CD68", "CD8")

for(marker in markers){
  trainData <- createFoldData(dat=dataSchurch, 
                            slideTrain = trainSlides, 
                            marker = marker)
cv_model2 <- glmnet:::cv.glmnet(trainData[[2]], trainData[[3]], alpha = 1, nfolds = 5)
# find optimal lambda value that minimizes test MSE
best_lambda2 <- cv_model2$lambda.min
best_model2 <- glmnet::glmnet(trainData[[2]], trainData[[3]], alpha = 1, lambda = best_lambda2)
testData <- createFoldData(dat=dataSchurch, 
                          slideTrain = testSlides, 
                          marker = marker)
Yhat.test <- as.numeric(
  predict(best_model2,newx=testData[[2]],s= best_lambda2))

# slide-specific calibration
calibY <- c()
calibYhat <- c()
calibSlides <- c()
for(i in trainSlides){
  trainslidei <- setdiff(trainSlides,i)
  trainDatai <- createFoldData(dat=dataSchurch, 
                              slideTrain = trainslidei, 
                              marker = marker)
  
  # model with tumor info
  cv_model2 <- glmnet:::cv.glmnet(trainDatai[[2]], trainDatai[[3]], alpha = 1, nfolds = 5)
  # find optimal lambda value that minimizes test MSE
  best_lambda2 <- cv_model2$lambda.min
  best_model2 <- glmnet::glmnet(trainDatai[[2]], trainDatai[[3]], alpha = 1, lambda = best_lambda2)
  caliData <- createFoldData(dat=dataSchurch, 
                             slideTrain = i, 
                             marker = marker)
  Yhat <- as.numeric(
    predict(best_model2,newx=caliData[[2]],s= best_lambda2))
  
  calibY <- c(calibY, caliData[[3]])
  calibYhat <- c(calibYhat, Yhat)
  calibSlides <- c(calibSlides, rep(i, length(Yhat)))
}

################################
########## Use imimp ###########
################################


SlideGroup <- dataSchurch %>% group_by(File.Name, groups) %>% reframe()
calibSlides_CLR <- which(calibSlides %in% (unlist(subset(SlideGroup, groups==1, File.Name))))
calibSlides_DII <- which(calibSlides %in% (unlist(subset(SlideGroup, groups==2, File.Name))))

testSlidesAll <- dataSchurch$File.Name[dataSchurch$patients %in% testPatients]
testSlides_CLR <- which(testSlidesAll %in% (unlist(subset(SlideGroup, groups==1, File.Name))))
testSlides_DII <- which(testSlidesAll %in% (unlist(subset(SlideGroup, groups==2, File.Name))))

imp.bysample.CLR <-imimp(Yhat.test[testSlides_CLR], calibYhat[calibSlides_CLR],
                    calibY[calibSlides_CLR], cdeType = "bySample",
                    x.mar = 50, y.mar=100, 
                    sampleID=list(calibSlides[calibSlides_CLR], testSlidesAll[testSlides_CLR]))

imp.simple <- imimp(Yhat.test, calibYhat,
                    calibY, cdeType = "simple", x.mar = 50, y.mar=100)
imp.local<- imimp(Yhat.test, calibYhat,
                  calibY, cdeType = "local")
imp.bysample.DII<-imimp(Yhat.test[testSlides_DII], calibYhat[calibSlides_DII],
                    calibY[calibSlides_DII], cdeType = "bySample",
                    x.mar = 50, y.mar=100, 
                    sampleID=list(calibSlides[calibSlides_DII], testSlidesAll[testSlides_DII]))
# combine
imp.bySample <- matrix(NA, nrow=length(testSlidesAll), ncol=10)

imp.bySample[testSlides_CLR,] <- imp.list_CLR[[3]];imp.bySample[testSlides_DII,] <- imp.list_DII[[3]]
imp.list.strat <- list(Yhat.test, imp.simple, imp.local, imp.bySample)

save(imp.list.strat, file=paste0("~/ImageImputation/SchurchfitStrat", marker, ".RData"))

slides.vec <- dataSchurch$File.Name[dataSchurch$File.Name %in% testSlides]
# library(tidyverse)
# library(tidyr)
# library(tibble)
library(reshape2)
# detach(package:plyr)
yhat.test <- imp.list.strat[[1]]
imp.list.strat <- imp.list.strat[2:4]
quantile.list <- lapply(imp.list.strat, function(imp.mat){
  imp.df <- data.frame(imp.mat, slides=slides.vec)
  imp.df$groups <- dataSchurch$groups[which(dataSchurch$File.Name %in% testSlides)]
  imp.vec <- melt(as.data.table(imp.df), id.vars = c("slides","groups"), variable.name = "im")
  quantile.df <- as.data.frame(imp.vec %>%
                  group_by(slides, im, groups) %>%
                  reframe(quantile = scales::percent(c(0.9, 0.95, 0.99)),
                  value = quantile(value, c(0.9, 0.95, 0.99))))
  return(quantile.df)
})
quantile.list.df <- do.call(rbind, quantile.list)
quantile.list.df$methods <- rep(c("simple", "local", "bySample"), each=(nrow(quantile.list.df)/3))
quantile.imp.summary <- as.data.frame(quantile.list.df %>% group_by(quantile, im, groups, methods) %>% reframe(means=mean(value))
)
data.subset <- dataSchurch[which(dataSchurch$File.Name %in% testSlides),c(paste0("nzNorm_", marker), "File.Name", "groups")]
names(data.subset) <- c("value", "slides", "groups")
real.quantiles <- data.subset %>% 
  group_by(slides) %>%  
  reframe(groups=first(groups),
            quantile = scales::percent(c(0.9, 0.95, 0.99)),
            real_value = quantile(value, c(0.9, 0.95, 0.99)))
real.quantiles.summary <- as.data.frame(real.quantiles %>% group_by(quantile,groups) %>% summarise(means=mean(real_value), .groups = "keep")
)

yhat.subset <- data.subset
yhat.subset$value <- yhat.test
yhat.quantiles <- yhat.subset %>% 
  group_by(slides) %>%  
  reframe(groups=first(groups),
            quantile = scales::percent(c(0.9, 0.95, 0.99)),
            real_value = quantile(value, c(0.9, 0.95, 0.99)))

ll <- list(quantile.list.df, real.quantiles, yhat.quantiles)

save(ll, file = paste0("~/ImageImputation/plots/dataSchurchStrat", marker,"quantileIMP.RData"))
print(marker)
}

plot.df.list <- list()
for(marker in markers){
  load(paste0("~/ImageImputation/plots/dataSchurchStrat", marker,"quantileIMP.RData"))
  n.imp <- 10
  impQuantile <- ll[[1]]
  trueQuantile <- ll[[2]]
  se.sq <- function(a){sd(a)^2/length((a))}
    
  var.calc <- function(qunatiledf){
    # within imputation: formula 9.2
    n.slides <- unique(qunatiledf$slides)
    within.var <- as.data.frame(qunatiledf %>% group_by(methods, quantile, im)%>%dplyr::summarize(SEi = se.sq(value), .groups = "keep"))
    within.var.pool <- as.data.frame(within.var%>%group_by(methods, quantile)%>%dplyr::summarize(VARW = mean(SEi), .groups = "keep"))
    # between imputation: formula 9.3
    between.var <- as.data.frame(qunatiledf %>% group_by(methods, quantile, im)%>%dplyr::reframe(meanImp = mean(value), .groups = "keep"))
    between.var.pool <- as.data.frame(between.var%>%group_by(methods, quantile)%>%dplyr::summarize(VARB = var(meanImp), means=mean(meanImp), .groups = "keep"))
    # pool variance: formula 9.4
    library(dplyr)
    all.vars <- left_join(within.var.pool, between.var.pool, by=c("methods", "quantile"))
    all.vars$VARB <- all.vars$VARB
    all.vars$vars <- all.vars$VARW+all.vars$VARB*((n.imp+1)/n.imp)
    # calculate df
    source("~/ImageImputation/dfCalc.R")
    all.vars.df <- dfCalc(all.vars$VARB, all.vars$vars, n.imp ,length(testSlides), 1)
    all.vars$tval95 <- qt(0.975, all.vars.df)
    return(all.vars)
  }
  all.vars <- var.calc(qunatiledf=impQuantile)
  # real quantile mean and variance
  true.plot <- trueQuantile %>% group_by(quantile)%>%dplyr::summarise(means=mean(real_value), vars=se.sq(real_value), methods="true") %>% as.data.frame()
  true.plot$tval95 <- qt(0.975, (length(testSlides)-1))
  
  df.plot <- rbind(true.plot, all.vars[,c("methods", "quantile", "means", "vars", "tval95")])
  df.plot$sd <- sqrt(df.plot$vars)
  df.plot$marker <- marker
  plot.df.list[[marker]] <- df.plot
}
plot.markerAll.df <- do.call(rbind, plot.df.list) %>% as.data.frame()
plot.markerAll.df$methods <- factor(plot.markerAll.df$methods , levels = c("true", "simple", "local", "bySample"))
save(plot.markerAll.df, file="StratAllMarker.RData")
```

```{r fig.align="center", echo = FALSE,fig.height = 10, fig.width=7}
library(paletteer)
p <- ggplot() +
  geom_errorbar(data=plot.markerAll.df,aes(ymin=means-tval95*sd, ymax=means+tval95*sd, x=methods, color=methods), position=position_dodge(width=0.4),width=.15)+
  geom_point(data=plot.markerAll.df,aes(y=means, x=methods, color=methods), position=position_dodge(width=0.4))+
  facet_grid(marker~quantile, scales = "free")  +scale_x_discrete(guide = guide_axis(angle = 90))+
  ggtitle("Imputation Quantiles")+theme_ipsum(axis_text_size = 9)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) + scale_color_paletteer_d("nationalparkcolors::BryceCanyon")


ggsave(p, file=paste0("~/ImageImputation/figure/RubinPoolAllmarker.png"), width=6, height=8, dpi=300)
```


```{r}
quantile3 <- unique(quantile.list.df.strat$quantile)
source("~/ImageImputation/dfCalc.R")

library(gee)
library(geepack)
gee.diff.result <- list()
for (marker in markers){
  load(paste0("~/ImageImputation/plots/dataSchurchStrat", marker,"quantileIMP.RData"))
  n.imp <- 10
  quantile.list.df.strat <- ll[[1]]
  trueQuantile <- ll[[2]]
  yhatQuantile <- ll[[3]]
# imputation mean
impMeans <- as.data.frame(quantile.list.df.strat %>% group_by(quantile, slides, methods) %>% reframe(means=mean(value)))
SlidePatientGroup <- dataSchurch %>% group_by(patients, File.Name, groups) %>% reframe()
impMeans <- left_join(impMeans, SlidePatientGroup, by=join_by(slides==File.Name))

trueQuantile <- left_join(trueQuantile, SlidePatient, by=join_by(slides==File.Name))

yhatQuantile <- left_join(yhatQuantile, SlidePatient, by=join_by(slides==File.Name))

df.plot <- data.frame(quantile=rep(c("90%", "95%", "99%"), 5),
                      means=NA, sd=NA, 
                      methods=rep(c("true", "mean","simple" , "local" , "bySample"), each=3))

df.plot.geemean <- df.plot[,c("quantile", "means", "sd","methods")]


# pool parameter estimates with Rubin's:
# mean: mean parameter estimate
# VarB: the variance of parameter estimate mean, of each imputation
# VarW: the mean of parameter estimate variance, of each imputation
quantile.list.df.strat <- left_join(quantile.list.df.strat, SlidePatient, by=join_by(slides==File.Name))

gee.results <- list()
df.plot.geediff <- df.plot[,c("quantile", "means", "sd","methods")]
df.plot.geediff$df <- NA

for(i in quantile3){
  m0 <- gee(real_value ~ groups, id=patients, family='gaussian',
            corstr = "exchangeable", data=subset(trueQuantile, quantile==i))
  idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods=="true"
  df.plot.geediff$means[idx] <- m0$coefficients[2]
  df.plot.geediff$sd[idx] <- sqrt(m0$robust.variance[2,2])
  df.plot.geediff$df[idx]<- 44-2
  df.plot.geediff$tval95[idx]<- qnorm(0.975)
  m0 <- gee(real_value ~ groups, id=patients, family='gaussian',
            corstr = "exchangeable", data=subset(yhatQuantile, quantile==i))
  idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods=="mean"
  df.plot.geediff$means[idx] <- m0$coefficients[2]
  df.plot.geediff$sd[idx] <- sqrt(m0$robust.variance[2,2])
  df.plot.geediff$df[idx]<- 44-2
  df.plot.geediff$tval95[idx]<- qnorm(0.975)
  for(m in c("simple", "local", "bySample")){
    n.imp <- length(levels(quantile.list.df.strat$im))
    m0.param <- data.frame(mean=rep(NA, n.imp), SE=rep(NA, n.imp))
    for(ii in 1:n.imp){
      m0 <- gee(value ~ groups, id=patients, family='gaussian', corstr = "exchangeable", 
            data=subset(quantile.list.df.strat, (quantile==i&methods==m&im==paste0("X",ii))))
      m0.param[ii,"mean"] <- m0$coefficients[2]
      m0.param[ii,"SE"] <- summary(m0)$coefficients[2,4]
    }
  idx <- df.plot.geemean$quantile==i&df.plot.geemean$methods==m
  df.plot.geediff$means[idx] <- mean(m0.param$mean)
  VARB <- var(m0.param$mean)
  vars <- sqrt(var(m0.param$mean)*(n.imp+1)/n.imp+mean((m0.param$SE)^2))
  df.plot.geediff$sd[idx] <- vars
  df.plot.geediff$df[idx]<- dfCalc(VARB, vars, 10 , 44, 2)
  df.plot.geediff$tval95[idx] <- qt(0.975, dfCalc(VARB, vars, 10 , 44, 2))
  }
  
}
df.plot.geediff$marker <- marker
gee.diff.result[[marker]] <- df.plot.geediff
}
gee.diff.result.df <- do.call(rbind, gee.diff.result)
gee.diff.result.df$methods <- ifelse(gee.diff.result.df$methods=="simple", "Method 1", 
                                     ifelse(gee.diff.result.df$methods=="local", "Method 2", 
                                            ifelse(gee.diff.result.df$methods=="bySample", "Method 3", 
                                                   ifelse(gee.diff.result.df$methods=="true", "True", "Mean"))))

gee.diff.result.df <- subset(gee.diff.result.df, methods != "Mean")

gee.diff.result.df$methods <- factor(gee.diff.result.df$methods, levels=c("True", "Method 1", "Method 2", "Method 3"))
library(paletteer)

p <- ggplot() +
  geom_errorbar(data=gee.diff.result.df,aes(ymin=means-tval95*sd, ymax=means+tval95*sd, x=methods, color=methods), position=position_dodge(width=0.4),width=.15)+
  geom_point(data=gee.diff.result.df,aes(y=means, x=methods, color=methods), position=position_dodge(width=0.4))+
  facet_grid(marker~quantile, scales = "free")  +scale_x_discrete(guide = guide_axis(angle = -90))+
  ggtitle("Quantile Difference between \nPatient Groups")+theme_ipsum(axis_text_size = 9)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) 


ggsave(p, file=paste0("~/ImageImputation/figure/RubinPoolGEEDiffAllmarker.png"), width=6, height=8, dpi=300)
```

